A Streaming Algorithm for 2-Center with Outliers in High Dimensions

### 2015-05-03 paper.tex
Last submission

Our query algorithm is presented in \Cref{alg:query}.
The idea behind the algorithm is as follows.
By our initial assumption about $p_1$ and by invariants (c), 
we know that $B_1$ completely contains $B_1^*$.
%because $B_1 \cap B_2^* = \emptyset$ . 
But for $B_2$, it might be the case that our assumption about $c_2$ 
was incorrect, and therefore, $B_2$ may not completely contain $B_2^*$. 
To overcome this issue, we try all possible candidates for $c_2$,
and compute, for each possible combinations of 
$B_1$, $B_2$, and Buffer, the best solution for 2-center with $z$ outliers
using the \textproc{MinCover} function presented in \Cref{alg:compute-min}.

@@

%Now, we show that the query algorithm correctly considers all possible candidates for $c_2$.
Let $C$ denote the set of candidates for $c_2$.
By invariant~(c), we know that $B_1 \cap B_2^* = \emptyset$. 
Therefore, there exists a point in $(B_2 \cup \Buffer) \cap B_2^*$,
and hence, $C$ is $(B_2 \cup \Buffer) \cap B_2^*$ in general.
%We now use the following lemma.
%In this general case, our candidates $C$ for $c_2$ is set $(B_2 \cup \Buffer) \cap B_2^*$.
However, when $|B_2| \geq \dz$, 
we show in the following lemma that $(\{c_2\} \cup \Buffer) \cap B_2^* \neq \emptyset$. 
Therefore, if $|B_2| \ge \dz$, 
we only need to consider $\{c_2\} \cup \Buffer$ as candidates for $C$.
%our candidates for $C$ are only $\{c_2\} \cup \Buffer$.

>>>>

Our query algorithm is presented in \Cref{alg:query}.
The idea behind the algorithm is as follows.
By our initial assumption about $p_1$ and  by invariants (c) and (d), 
if $c_p \in B_2^*$, then we know that $B_1$ completely contains $B_1^*$,
and $B_2$ completely contains $B_2^*$.
%because $B_1 \cap B_2^* = \emptyset$ . 
However, it might be the case that our assumption about $c_p$ 
was incorrect, and therefore, $B_1$ (resp., $B_2$) 
may not completely contain $B_1^*$ (resp., $B_2^*$). 
To overcome this issue, we try all possible candidates for $c_2$
(which in turn, determines $c_p$),
and compute, for each resulting partition of $P$ into 
$B_1$, $B_2$, and Buffer, the best solution for 2-center with $z$ outliers
using the \textproc{MinCover} function presented in \Cref{alg:compute-min}.

@@

%Now, we show that the query algorithm correctly considers all possible candidates for $c_2$.
Let $C$ denote the set of candidates for $c_2$.
By invariant~(c), we know that $B_1 \cap B_2^* = \emptyset$. 
Therefore, there exists a point in $(B_2 \cup \Buffer) \cap B_2^*$,
and hence, $C$ is $(B_2 \cup \Buffer) \cap B_2^*$ in general.
%We now use the following lemma.
%In this general case, our candidates $C$ for $c_2$ is set $(B_2 \cup \Buffer) \cap B_2^*$.
However, when $|B_2| \geq \dz$, 
we will show in the following lemma that $(\{c_2\} \cup \Buffer) \cap B_2^* \neq \emptyset$. 
Therefore, if $|B_2| \ge \dz$, 
we only need to consider $\{c_2\} \cup \Buffer$ as candidates for $C$.
%our candidates for $C$ are only $\{c_2\} \cup \Buffer$.
